Increasingly sensors are added in our surroundings. 
The list of sensors in our phones increases all the time, and new "smart" products keeps popping
up everywhere.
Products that promises everything from optimizing your sleep through monitoring how you
sleep\cite{wareable}, to promising better teeth with monitoring your toothbrush\cite{toothbrush}
can now be bought.

Also our environment is going through an digital revolution where houses, cars, playgrounds
and nearly everything are becoming online, smart and data collecting.
Internet of Things -IoT, and Big Data are the buzz words of todays modern world, and this
revolution of data gathering and processing opens up many new possibilities.

The more detailed information there is available about our environment the more context aware
our application can bacome, by better integrating the technology in our environments and provide
smother interaction with the user(s).

The world however, isn't at that exact point just yet. 
Even a basic task as simple gathering all our data in one place seems in general to be an
unsolved task.
A task that needs to be solved over and over every time a new device comes out or whenever
a system is migrated from one environment to another environment. 
There seems to always be manual integration and setup of a software system in its environment
where people have to fiddle with endless configuration files.

To solve the problem there are two possible approaches:
\begin{itemize}
\item Make more generalized software systems
\item Make more customizable software systems
\end{itemize}

By making a more generalized system there will be less manual plumbing when integrating the
system in an environment. 
However knowing all diversities, variations or problems before designing a system is a tough
challenge, that has the risk of generating a too generalized solution to the given problem.

In this report the focus will be laid upon a more customizable approach.
More specific the report will describe the design, development and evaluation of a Domain Specific
Language(DSL) for building and customizing dashboards for gathering information from the internet
of things and visualizing the information through the dashboards. 
The project example program will focus on information gathered from different sensors in
building OU44.

\textbf{Buildings}\\
The first step towards automation of buildings and homes with Internet of Things is to
understand the data provided. 
Through understanding the provided data it is possible to decide which actions to take, based on
one or more sensor inputs. 
Making decisions and taking action for one building is not generalizable enough to apply to
other buildings without customization. 
Further are actions rooted in a problem that needs to be solved. 
This means that customization is needed whenever one of the following is true:
\begin{itemize}
\item Problems that needs to be solved might differ from one building to another building
\item The buildings infrastructure might not be the same between buildings meaning that the solution might differ
\item Context of the environment have changed
\end{itemize}

In general there is a great need for customization or customizable application in building
automation through Internet of Things.

Using charts or graphs to visualize large amounts of complex data is easier than poring over
the data itself. 
Data visualization is a quick, easy way to convey concepts in a universal manner.
Datavisualization can be used for different purposes. 
Some of these are:
\begin{itemize}
\item Decision making
\item Identify areas that need attention or improvement
\item Clarify which factors influence behaviuor
\item Identify behaviour or patterns
\end{itemize}

The problem is that a visualisation is not universal in sense of the purposes it can be used for. 
Therefore, there are a great need for customized or customizable visualizations that supports
the different purposes. 

The purpose in the project is to have a website, with responsive design, which can be viewed on any browser like Mobile, Desktop, Laptop and tablet. 
The pages on the website will contain Links between the pages on the webpage. 
It will also be possible to link to external webpages. 
Additionally the pages will contain graphs and tables which shows data. 
The data will either be fetched from external sources or external sources will have the
possibility to post data to a data source given a predefined data schema. 

Data in data sources can be transformed using formula expressions and have to go through at
least one formula expression in order to be displayed on a graph.  


In order to enable the user to create the above in a easy customizable way two domain specific
languages will be created and used.


